---
title: "Robinhood Question"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(latex2exp)
```

## Problem Statement
> You start with $30. Flip a coin - win $1 for heads, lose $1 for tails. What's the probability that you win $100?
> Possible answers are 20%, 25%, 30%, 40%

## Interpreting the Problem
Likely they meant to say

* It's a fair coin (50% heads, 50% tails)
* If your balance reaches $0, you lose, end of game
* replace "you win $100" with "your balance reaches $100"

With these assumptions, it's a straightforward formulation of the Gambler's Ruin problem

Here's a nice analysis of that problem: 
http://www.columbia.edu/~ks20/FE-Notes/4700-07-Notes-GR.pdf

From this we have a formula:

$P_{i}^{N}(p) = \frac{1 - (\frac{q}{p})^i}{1 - (\frac{q}{p})^N}$

Where $i$ is the starting balance, $p$ is the probability of heads, $q = 1 - p$, $N$ is the target balance.

If $p = q$ (fair coin), there's a simpler formula:

$P_{i}^{N} = \frac{i}{N}$

For this problem,

$p$ is 0.5, the probability of heads

$i = 30$ (starting balance)

$N = 100$ (target balance)

$q = 1 - p$

Substituting,

$P_{30} = \frac{30}{100} = 0.3$

30%!

## Yes, But

They never did say "fair coin". As $p$ ranges from 0 to 1, what happens to our odds?

Turns out, if the coin is only a little away from fair, the outcome is quite certain. Closer in on 50/50, though, we see some variation.

```{r echo=F}
i = 30
N = 100
x_low = .475
x_high = .55
f <- function(p) ifelse(p == 0.5, i / N, (1 - ((1 - p) / p) ^ i)/ (1 - ((1 - p) / p) ^ N))
p <- ggplot(data = data.frame(p = 0), mapping = aes(x = p)) +
  scale_x_continuous(breaks = seq(x_low, x_high, 0.025), limits = c(x_low, x_high)) +
  scale_y_continuous(breaks = seq(0, 1, 0.1)) +
  ylab(TeX("$P_{30}^{100}(p)$")) 

p1 <- p + stat_function(fun=f)
print(p1)
```

There's a coin that matches each of the given answers. Instead of doing math, we can read it off of the graph:
```{r echo=F}
x_low = .497
x_high = .5025
p <- ggplot(data = data.frame(p = 0), mapping = aes(x = p)) +
  scale_x_continuous(breaks = seq(x_low, x_high, 0.00025), limits = c(x_low, x_high)) +
  scale_y_continuous(breaks = seq(0, 1, 0.05)) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  geom_hline(yintercept=0.2, linetype="dashed", color = "red") +
  geom_hline(yintercept=0.25, linetype="dashed", color = "red") +
  geom_hline(yintercept=0.3, linetype="dashed", color = "red") +
  geom_hline(yintercept=0.4, linetype="dashed", color = "red") +
  ylab(TeX("$P_{30}^{100}(p)$")) 

p2 <- p + stat_function(fun=f)
print(p2)
```

## Gambler's Ruin: p Really Matters
Reading off of the graph, I get (approximately):

$P_{30}(0.497375) = 0.2$

$P_{30}(0.49875) = 0.25$

$P_{30}(0.5) = 0.3$

$P_{30}(0.50225) = 0.4$
